Approximation as Differentiation

### 2025-04-29 appendix/notes/language.tex
Move syntax fig to notes.
Make a start on syntax.

\section{Language}

@@

We parameterise our language over a signature $\Sigma = (S, \phi, R)$ consisting of:
\begin{itemize}
\item a set $S$ of sorts
\item a set of operations $\phi$ with signature $\Sigma(\phi) \in S^* \times S$
\item a set of relations $R$ with signature $\Sigma(R) \in S^*$
\end{itemize}

\subsection{Semantic domain}

We interpret our language into any category with:
\begin{itemize}
\item finite products (binary products and a terminal object)
\item Booleans
\end{itemize}
\note{Ignoring lists for now. Booleans can be derived from coproducts.}

>>>>

\section{Language Syntax and Interpretation}

@@

We assume a language parameterised by a signature $\Sigma = (S, \Op, \Rel)$ consisting of:
\begin{itemize}
\item a set $S$ of sorts;
\item a set $\Op(s_1, \ldots, s_n; s)$ of operations with input sorts $s_1, \ldots, s_n$ and output sort $s$;
\item a set $\Rel(s_1, \ldots, s_n)$ of $n$-ary relations over sorts $s_1, \ldots, s_n$
\end{itemize}

\noindent \todo{Are relations just for examples -- perhaps not needed in the formalism?}

\input{fig/syntax}

% \subsection{Semantic domain}
%
% We interpret our language into any category with:
% \begin{itemize}
% \item finite products (binary products and a terminal object)
% \item Booleans
% \end{itemize}
% \note{Ignoring lists for now. Booleans can be derived from coproducts.}
